Long term cloud enhancement events of global solar irradiance over Thessaloniki

### 2024-06-04 GHI_enh_04_investigate.tex
Commit 2024-05-23 10:10
Commit 2024-05-23 12:14
Commit 2024-05-23 16:10
Commit 2024-05-24 12:16
Commit 2024-06-04 19:13

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-20}

@@

@@

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-9} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_multi-1} \end{center}

@@

\begin{verbatim}
2024-05-20 16:56:07.0 athan@tyler GHI_enh_04_investigate.R 1.334659 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-04}

@@

{[}1{]} 0.8092946

@@

\textbf{@Martins2022}

@@

@@

@@

\begin{verbatim}
2024-06-04 15:58:17.7 athan@tyler GHI_enh_04_investigate.R 2.098396 mins
\end{verbatim}

### 2024-06-04 article/article.tex
Commit 2024-06-04 19:13

@@

\caption{Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March. The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the maximum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies-ECE}
\end{figure}

>>>>

{\centering \includegraphics[width=1\linewidth]{../images/P_energy-7}

\caption{Trends of the mean OIR per CE.}\label{fig:P-energy-mean}
\end{figure}

@@

\caption{Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March. The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the max imum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies-ECE}
\end{figure}
